---
title: "Watershed-scale Analysis of SAR and High-Priority Waterbodies"
author: "Chris Madsen and John Phelan"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  pdf_document: default
editor_options:
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 12, fig.height = 8)
library(tidyverse)
library(sf) # shapes
library(viridis) # colors
library(bcdata)
library(bcmaps)
library(raster)
library(geodata)
library(dismo) # getting the climate models and other cool things
library(ggpattern) # hatching ggplot
library(RColorBrewer) # colors
library(ggspatial) # scale bar
library(patchwork) # For combining ggplot figures in cool ways
library(leaflet)
library(gdalUtilities)

path_to_user = str_extract(getwd(), ".*Users/[A-Z]+")
onedrive_path = paste0(path_to_user,"/OneDrive - Government of BC/data/CNF/")

redo_downstream = FALSE
```

Background: This assessment uses the high-priority waterbodies as defined by the Zebra-Quagga Mussel Prioritization Model (2024 edition), DFO SARA-listed species occurrence data and critical habitat data, and BC Data Catalogue SPI data for Sockeye Salmon and Bull Trout to assess overlap between 5 species (4 SARA-listed species and Sockeye Salmon) and the high-priority waterbodies. More detail below.

Note: At present, no DFO data exists for Bull Trout population of South Coast, nor for Sockeye Salmon population at Cultus Lake; thus, we turned to the BC Data Catalogue and research-grade iNaturalist reports for those two species.

Note: We also sought records for these five target species in the [provincial Species-at-risk layer](https://catalogue.data.gov.bc.ca/dataset/species-and-ecosystems-at-risk-publicly-available-occurrences-cdc); only one species was present in this dataset (Rocky Mountain Ridged Mussel), with a single observation that was not already present in the DFO SARA dataset.

## Data {.tabset}
```{r reading_in_data}
# Zebra Quagga Prioritization Model

zqpm <-read_sf(paste0(onedrive_path,"waterbodies_zqm_shortlist_risk_estimates.gpkg"))

# Watersheds of some scale
if(!file.exists(paste0(onedrive_path,'watershed_groups.gpkg'))){
  ws = bcdc_query_geodata('freshwater-atlas-watershed-groups') %>%   
    # This one has 246 rows
    collect()
  # Simplify the geometry! Woo
  ws_s = rmapshaper::ms_simplify(ws)
  sf::write_sf(ws_s,paste0(onedrive_path,'watershed_groups.gpkg'))
} else {
  ws = sf::read_sf(paste0(onedrive_path,'watershed_groups.gpkg'))
}

# Regions (just in case)
regs = bcmaps::nr_regions()

if(!file.exists(paste0(onedrive_path,"dfo_sara_and_crit_hab_and_sockeye_data.gpkg"))){
  
  # SAR layer in BC Data Catalogue - does it have our species?
  prov_sar = bcdc_query_geodata('species-and-ecosystems-at-risk-publicly-available-occurrences-cdc') |> 
    filter(SCI_NAME %in% c("Cottus aleuticus","Oncorhynchus clarkii lewisi",
                           "Salvelinus confluentus","Gonidea angulata",
                           "Oncorhynchus nerka")) |> 
    collect() |> 
    sf::st_transform(3857)
  
  # DFO SARA spatial data.
  sara = read_sf(paste0(onedrive_path,"dfo_occurrences_in_BC_all_species.gpkg"))
  
  # Filter SARA occurrence data by scientific name AND population, in one fell swoop.
  sara = sara |> 
    dplyr::filter(Scientific_Name == "Cottus aleuticus" & str_detect(Population_EN, 'Cultus') |
                    Scientific_Name == "Oncorhynchus clarkii lewisi" & str_detect(Population_EN,'Pacific') | 
                    Scientific_Name == "Salvelinus confluentus" & str_detect(Population_EN,'South Coast') |
                    Scientific_Name == "Gonidea angulata")
  
  # Make sure the prov_sar data is distinct from stuff in the SARA data.
  non_distinct_rows = as.data.frame(st_intersects(prov_sar, sara)) |> 
    dplyr::select(row.id) |> 
    dplyr::distinct() |> 
    dplyr::pull(row.id)
  
  prov_sar_distinct = prov_sar[-non_distinct_rows,]
  
  # Get values for columns that sara has.
  info_for_prov_sar = sara |> 
    dplyr::filter(Scientific_Name %in% prov_sar_distinct$SCI_NAME) |> 
    sf::st_drop_geometry() |> 
    dplyr::select(Common_Name_EN, Scientific_Name, Population_EN, Taxon) |> 
    dplyr::distinct()
  
  prov_sar_distinct = prov_sar_distinct |> 
    dplyr::rename(Scientific_Name = SCI_NAME,
                  geom = geometry) |> 
    dplyr::left_join(info_for_prov_sar) |> 
    dplyr::select(names(info_for_prov_sar))
  
  sara = sara |> 
    dplyr::bind_rows(prov_sar_distinct)
  
  # sara |> st_drop_geometry() |> count(Scientific_Name, Population_EN)
  
  sockeye = bcinvadeR::grab_aq_occ_data('sockeye salmon')
  
  bulltrout = bcinvadeR::grab_aq_occ_data('bull trout')
  
  # Ensure the geometry column has the right name!
  sockeye = sockeye |> rename(geom = geometry)
  bulltrout = bulltrout |> rename(geom = geometry)

  # Filter Sockeye for just Cultus lake.
  cultus = bcdc_query_geodata('freshwater-atlas-lakes') |> 
    filter(GNIS_NAME_1 == 'Cultus Lake') |> 
    collect() |> 
    sf::st_transform(st_crs(sockeye))
  
  sockeye = sockeye |> 
    sf::st_filter(cultus)
  
  # Filter bulltrout for just south coast
  regs = bcmaps::nr_regions()
  south_coast = regs[regs$ORG_UNIT_NAME == "South Coast Natural Resource Region",]
  south_coast = sf::st_transform(south_coast, st_crs(bulltrout))
  
  bulltrout = bulltrout |> 
    sf::st_filter(south_coast)
  
  # Prepare sockeye and bulltrout for binding to SARA data.
  sockeye_for_bind = sockeye |> 
    dplyr::mutate(Population_EN = 'Cultus',
                  Common_Name_EN = 'Sockeye Salmon',
                  Scientific_Name = 'Oncorhynchus nerka',
                  Taxon = 'Fishes') |> 
    dplyr::select(Population_EN, Common_Name_EN, Scientific_Name, Taxon) |> 
    sf::st_transform(3857)
  
  bulltrout_for_bind = bulltrout |> 
    dplyr::mutate(Population_EN = 'South Coast',
                  Common_Name_EN = 'Bull Trout',
                  Scientific_Name = 'Salvelinus confluentus',
                  Taxon = 'Fishes') |> 
    dplyr::select(Population_EN, Common_Name_EN, Scientific_Name, Taxon) |> 
    sf::st_transform(3857)
  
  # Merge sockeye with SARA
  occdat = sara |> 
    dplyr::bind_rows(sockeye_for_bind) |> 
    dplyr::bind_rows(bulltrout_for_bind)
  
  ### Critical habitat
  critHab<-read_sf(paste0(onedrive_path,"federal_critical_habitat.gpkg"))
  
  # Make sure column names are the same between critical habitat and SARA occ object.
  ensure_multipolygons <- function(X) {
    tmp1 <- tempfile(fileext = ".gpkg")
    tmp2 <- tempfile(fileext = ".gpkg")
    st_write(X, tmp1)
    ogr2ogr(tmp1, tmp2, f = "GPKG", nlt = "MULTIPOLYGON")
    Y <- st_read(tmp2)
    st_sf(st_drop_geometry(X), geom = st_geometry(Y))
  }
  
  critHabFixed<-ensure_multipolygons(critHab)
  
  critHab_sciFilt<-critHabFixed %>% 
    dplyr::filter(Scientific_Name == "Cottus aleuticus" & str_detect(Population_EN, 'Cultus') |
                    Scientific_Name == "Oncorhynchus clarkii lewisi" & str_detect(Population_EN,'Pacific') | 
                    Scientific_Name == "Salvelinus confluentus" & str_detect(Population_EN,'South Coast') | 
                    Scientific_Name == "Gonidea angulata")
  #unique(critHab$Common_Name_EN)
  
  
  # critHabTrans<-st_transform(critHab_sciFilt, st_crs(occdat))
  mergedPopn<-bind_rows(occdat, critHab_sciFilt)
  
  # ggplot() + geom_sf(data = bcmaps::bc_bound()) + 
  #   geom_sf(data = mergedPopn)
  # Do st_difference with bc polygon.
  mergedPopn = ensure_multipolygons(mergedPopn)
  
  mergedPopn = sf::st_make_valid(mergedPopn)
  
  mergedPopn_d = sf::st_difference(mergedPopn, bcmaps::bc_bound() |> dplyr::summarise() |> sf::st_transform(3857))
  
  ggplot() + geom_sf(data = mergedPopn)
  
  sf::write_sf(mergedPopn, paste0(onedrive_path,"dfo_sara_and_crit_hab_and_sockeye_data.gpkg"))
} else {
  mergedPopn = read_sf(paste0(onedrive_path,"dfo_sara_and_crit_hab_and_sockeye_data.gpkg"))
}

mergedPopn = sf::st_transform(mergedPopn, 3005)


```

### DFO and Sockeye Data Summary
```{r dfo_and_sockeye_data_summary}
mergedPopn |> 
  sf::st_drop_geometry() |> 
  # dplyr::select(Common_Name_EN, Scientific_Name, Population_EN) |> 
  dplyr::count(Common_Name_EN, Scientific_Name, Population_EN, name = 'Occurrences') |> 
  knitr::kable()
```

```{r filter_destination_waterbodies_and_find_downstream_networks_for_each}

zqpmUseFilt<-zqpm %>% arrange(desc(InvasionRisk)) %>% 
  dplyr::select(WATERSH, WATERBO, GNIS_NA, InvasionRisk) %>% 
  filter(!GNIS_NA %in% c("Dry Storage", "Pacific Ocean")) 
 
# Summarise the SARA-listed, Whirling-Disease-sensitive fish species by subwatershed.


sara_by_wb = mergedPopn %>%
  st_transform(3005) %>% 
  st_simplify() %>% 
  st_join(zqpmUseFilt %>% dplyr::select(GNIS_NA, WATERBO)) %>% 
  sf::st_drop_geometry() %>% 
  dplyr::select(Scientific_Name,Common_Name_EN,GNIS_NA, WATERBO)

sara_by_wb = sara_by_wb %>%
  dplyr::filter(!is.na(GNIS_NA)) |> 
  dplyr::distinct() %>% 
  dplyr::add_count(GNIS_NA, WATERBO, name = 'number_distinct_SAR') |> 
  dplyr::group_by(GNIS_NA,number_distinct_SAR, WATERBO) |> 
  dplyr::summarise(SARA_species = paste0(Common_Name_EN, collapse = ', ')) 

zqpmUseFilt = zqpmUseFilt %>% 
  dplyr::left_join(sara_by_wb) |> 
  dplyr::mutate(number_distinct_SAR = replace_na(number_distinct_SAR, 0),
                SARA_species = replace_na(SARA_species, 'None'))
  
# Maybe to change here: drop bin 2 priority waterbodies
# if they do not overlap with the species-at-risk data.
zqpmUseFilt = zqpmUseFilt |> 
  dplyr::filter(number_distinct_SAR > 0)

# Use suppressMessages just in case the bcmaps package is feeling chatty.
bc <- suppressMessages(bc_bound())
```

### Visualized Data {.tabset}

#### High-Priority Waterbodies from ZQM Model
Lowest risk factor is 1, and increases to maximum risk of 3
```{r high_Priority_waterbodies_by_Subwatershed}

# Combine the waterbodies flagged as high risk by the ZQ Mussel Prioritization Model with the downstream sections we found above; this allows us to plot a single sf object to the plot below and utilize a legend to easily explain what is what.

priority_wb_and_ds = dplyr::bind_rows(
  # ds_geom_sum |> 
  #   dplyr::rename(geom = geometry) |> 
  #   dplyr::mutate(type = "Downstream\nNetwork"),
  zqpm |> 
    dplyr::mutate(type = "High-priority\nWaterbody")
) |> 
  arrange(type)

# # make map insert of BC with region highlighted.
# map_inset = ggplot() + 
#   geom_sf(data = bc) + 
#   # geom_sf(data = dplyr::summarise(ws_high_priority), fill = 'purple') +
#   geom_sf(data = priority_wb_and_ds, col = 'red') +
#   ggthemes::theme_map() + 
#   theme(plot.background = element_rect(color = 'black'))

main_map = ggplot() +
  geom_sf(data = bc) +
  # geom_sf(data = ws_background, fill = "lightgrey")+ # simplify geom?
  # geom_sf(data=ws_high_priority, fill = "purple", color = "black", alpha = 0.3)+
  # geom_sf(data=ds_geom_sum, fill = "orange", color="orange")+
  # geom_sf(data=zqpmUseFilt, fill = "red", color="darkred")+
  geom_sf(data = priority_wb_and_ds,aes(fill = as.factor(InvasionRisk), col = as.factor(InvasionRisk))) +
  # scale_fill_manual(values = c("Downstream\nNetwork" = "orange",
  #                              "High-priority\nWaterbody" = "red")) +
  # scale_colour_manual(values = c("Downstream\nNetwork" = "orange",
  #                              "High-priority\nWaterbody" = "red")) +
  scale_fill_manual(values = c("1" = "lightblue", "2" = "orange", "3" = "red"))+
  scale_colour_manual(values = c("1" = "lightblue", "2" = "orange", "3" = "red"))+
  labs(title = paste0("High-priority Waterbodies Flagged by ZQM Model"),
       subtitle = paste0("Waterbody count (N = ",nrow(zqpm),")"),
       # subtitle = paste0("This includes downstream networks. \nTotal number of subwatersheds: ",nrow(ws_high_priority)),
       fill = "ZQM Risk Factor",
       colour = "ZQM Risk Factor")+
  ggthemes::theme_map()+
  theme(plot.title = element_text(size = rel(2), face = "bold"),
        plot.subtitle = element_text(size = rel(1.8)),
        legend.title = element_text(size = rel(1.8)),
        legend.text = element_text(size = rel(1.2)),
        legend.position = 'right'
  ) + 
  coord_sf(xlim = sf::st_bbox(priority_wb_and_ds)[c(1,3)],
           ylim = sf::st_bbox(priority_wb_and_ds)[c(2,4)]) + 
  ggspatial::annotation_scale()

# The following code to combine plots uses the {patchwork} package.
# if(!interactive()) {
#   main_map + patchwork::inset_element(map_inset, right = 1, top = 1, left = 0.8, bottom = 0.75)
# }
main_map
```

#### Occurrence of Five Target Species
```{r}

labelpoint<-mergedPopn[mergedPopn$Common_Name_EN == "Sockeye Salmon", ][1,]
ggplot() + 
  geom_sf(data = bc |> sf::st_transform(sf::st_crs(mergedPopn)), alpha = 0.25) +
  geom_sf(data = mergedPopn, aes(color = Common_Name_EN, fill = Common_Name_EN))+
ggrepel::geom_label_repel(data = labelpoint, 
                  aes(label = "Sockeye Salmon and Cultus Pygmy Sculpin", geometry = geom),stat = 'sf_coordinates', size = 3, nudge_y = -22000) +
  coord_sf(xlim = sf::st_bbox(st_buffer(mergedPopn,100000))[c(1,3)],
           ylim = sf::st_bbox(st_buffer(mergedPopn,100000))[c(2,4)]) +
  # theme(legend.position = 'none') +
  labs(title = 'Distribution of Five Target Species in BC',
       fill = "Species Common Name",
       colour =  "Species Common Name") +
  #::theme_map() + 
  theme(plot.title = element_text(size = rel(2), face = "bold"),
        plot.subtitle = element_text(size = rel(1.8)),
        legend.title = element_text(size = rel(1.3)),
        legend.text = element_text(size = rel(1)),
        panel.background = element_blank(),
        legend.position = 'bottom',
        
  )
  
```

## Results {.tabset}

### Provice-wide Overlap of Target Species and Priority Waterbodies {.tabset}

#### Map
```{r number_of_distinct_SAR_species_by_Subwatershed}
#sp_colors<-c( "#EFFDB1ff","#BDD793ff","#8BB174ff","#598B56ff","#276537ff")
cols_overlap <- c("#007bff", "#ff7f00", "#228b22", "purple")
#cols<-col_ramp(4)

# We could trim the geometry of the Fraser River to just include the south coast region,
# which is what we used to filter Bull trout records anyways since that's the only
# population we want to assess.

southcoast = suppressMessages(bcmaps::nr_regions())
southcoast = southcoast[southcoast$REGION_NAME == 'South Coast Natural Resource Region',]

fraser = zqpmUseFilt[zqpmUseFilt$GNIS_NA == 'Fraser River',]
fraser_clipped = sf::st_intersection(fraser, southcoast)

zqpmUseFilt = zqpmUseFilt |> 
  dplyr::filter(GNIS_NA != 'Fraser River') |> 
  dplyr::bind_rows(fraser_clipped)

g = ggplot() + 
  geom_sf(data = bc, alpha = 0.25) +
  geom_sf(data = priority_wb_and_ds, col = 'grey') +
  geom_sf(data = zqpmUseFilt, 
          aes(fill = SARA_species,
              colour = SARA_species), lwd = 1.8) + 
  scale_fill_manual(values =  cols_overlap, na.value = "grey")+
  scale_colour_manual(values =  cols_overlap, na.value = "grey")+
  labs(title = 'Number of Distinct SARA-listed Species by Priority Waterbody',
       subtitle = paste0("Waterbody count (N = ",nrow(zqpmUseFilt),")"),
       fill = "Species Common Name",
       colour =  "Species Common Name") +
  # ggthemes::theme_map()+
  theme(plot.title = element_text(size = rel(2), face = "bold"),
        plot.subtitle = element_text(size = rel(1.8)),
        legend.title = element_text(size = rel(1.8)),
        legend.text = element_text(size = rel(1.2)),
        panel.background = element_blank()
        ) +
  coord_sf(xlim = sf::st_bbox(priority_wb_and_ds)[c(1,3)],
           ylim = sf::st_bbox(priority_wb_and_ds)[c(2,4)]) + 
  ggspatial::annotation_scale()


if(!interactive()) {
  print(g)
}

```

#### Table
```{r}
## Waterbody by species
DT::datatable(
  zqpmUseFilt |>
    sf::st_drop_geometry() |>
    dplyr::select(-WATERSH, -WATERBO) |>
    dplyr::mutate(number_distinct_SAR = replace_na(number_distinct_SAR, 0)) |>
    dplyr::mutate(SARA_species = replace_na(SARA_species, "None")) |> 
    dplyr::select(`Waterbody Name` = GNIS_NA,
                  InvasionRisk,
                  `Number of SARA-listed Species` = number_distinct_SAR,
                  `SARA-listed species` = SARA_species),
    options = list(
            columnDefs = list(list(className = 'dt-center', targets = 0:4))
            )
)
```

### Overlap in Columbia and Fraser River Watersheds {.tabset}
```{r filter_overlap_to_regions}
fras = sf::read_sf("W:/CMadsen/shared_data_sets/fraser_watershed_priority_area.gpkg") |>
dplyr::summarise() |> 
  dplyr::mutate(watershed = 'Fraser')

columbia = sf::read_sf("W:/CMadsen/shared_data_sets/columbia_watershed_priority_area.gpkg") |>
dplyr::summarise() |> 
  dplyr::mutate(watershed = 'Columbia')

watersheds = dplyr::bind_rows(fras, columbia) |>
  # dplyr::summarise() |> 
  sf::st_transform(3005)

zqpm_in_watersheds = zqpmUseFilt |> 
  sf::st_join(watersheds)

# zqpm_in_watersheds |> 
#   st_drop_geometry() |> 
#   count(GNIS_NA,watershed) |> 
#   View()
# zqpm_in_watersheds = sf::st_intersection(
#   zqpmUseFilt,
#   watersheds 
# )

```

#### Map
```{r results_as_map}
g = ggplot() + 
  geom_sf(data = bc, alpha = 0.25, fill = 'grey') +
  geom_sf(data = priority_wb_and_ds, col = 'grey') +
  geom_sf(data = fras, col = 'grey', fill = 'white') +
  geom_sf(data = columbia, col = 'grey', fill = 'white') +
  geom_sf(data = zqpm_in_watersheds,
          aes(fill = SARA_species,
              colour = SARA_species), lwd = 1.8) + 
  scale_fill_manual(values =  cols_overlap, na.value = "grey")+
  scale_colour_manual(values =  cols_overlap, na.value = "grey")+
  labs(title = 'Number of Distinct SARA-listed Species by Priority Waterbody',
       subtitle = paste0("Waterbody count (N = ",nrow(zqpm_in_watersheds),")"),
       caption = "(Fraser and Columbia River Watersheds)",
       fill = "Species Common Name",
       colour =  "Species Common Name") +
  # ggthemes::theme_map()+
  theme(plot.title = element_text(size = rel(2), face = "bold"),
        plot.subtitle = element_text(size = rel(1.8)),
        legend.title = element_text(size = rel(1.8)),
        legend.text = element_text(size = rel(1.2)),
        panel.background = element_blank()
        ) +
  coord_sf(xlim = sf::st_bbox(watersheds)[c(1,3)],
           ylim = sf::st_bbox(watersheds)[c(2,4)]) + 
  ggspatial::annotation_scale()


if(!interactive()) {
  print(g)
}
```

#### Table
```{r results_as_table}
DT::datatable(
  zqpm_in_watersheds |>
    sf::st_drop_geometry() |>
    dplyr::select(-WATERSH, -WATERBO) |>
    dplyr::mutate(number_distinct_SAR = replace_na(number_distinct_SAR, 0)) |>
    dplyr::mutate(SARA_species = replace_na(SARA_species, "None")) |> 
    dplyr::select(Watershed = watershed,
                  `Waterbody Name` = GNIS_NA,
                  InvasionRisk,
                  `Number of SARA-listed Species` = number_distinct_SAR,
                  `SARA-listed species` = SARA_species),
    options = list(
            columnDefs = list(list(className = 'dt-center', targets = 0:4))
            )
)
```

## Appendix 
### Table of high-priority waterbodies
The shortlist of priority waterbodies consists of `r nrow(zqpm)` waterbodies. `r nrow(zqpmUseFilt)` of these waterbodies overlapped with at least one of the target species.

```{r}
DT::datatable(
  zqpm |> 
  sf::st_drop_geometry() |> 
  dplyr::select(GNIS_NA, InvasionRisk)
)
```

```{r}
### Interactive Map
# zqpm_wgs = sf::st_transform(zqpmUseFilt, 4326)
# 
# my_pal = leaflet::colorFactor(
#   palette = 'PRGn',
#   domain = as.factor(unique(zqpm_wgs$number_distinct_SAR))
# )
# 
# my_pal_l = leaflet::colorFactor(
#   palette = 'PRGn',
#   domain =  as.factor(unique(zqpm_wgs$number_distinct_SAR)),
#   reverse = T
# )
# 
# # Set colours manually
# zqpm_wgs = zqpm_wgs |> 
#   mutate(leaf_col = case_when(
#     number_distinct_SAR == 0 ~ 0,
#     number_distinct_SAR > 0 ~ 0.75
#   ))
# 
# my_tbls = leafpop::popupTable(
#   zqpmUseFilt |> 
#     sf::st_drop_geometry() |> 
#     dplyr::select(-WATERSH,-WATERBO)
#   )
# 
# leaflet(height = 600) |> 
#   addTiles() |> 
#   addProviderTiles(providers$Esri.OceanBasemap) |> 
#   addProviderTiles(providers$CartoDB) |> 
#   addPolylines(
#     data = zqpm_wgs,
#     label = ~paste0(GNIS_NA,": ",number_distinct_SAR),
#     popup = lapply(my_tbls, htmltools::HTML),
#     color = ~my_pal(number_distinct_SAR),
#     opacity = ~leaf_col
#   ) |> 
#   addLegend(
#     title = "Number of<br>Distinct SARA",
#     pal = my_pal_l,
#     values = unique(zqpm_wgs$number_distinct_SAR),
#     labFormat = labelFormat(transform = function(x) sort(x, decreasing = TRUE))
#   ) |> 
#   addScaleBar(position = 'bottomright')
```


```{r downstream_plot}
## Downstream Network Overlaps

# fras = sf::read_sf("W:/CMadsen/shared_data_sets/fraser_watershed_priority_area.gpkg") |>
# dplyr::summarise()
# 
# columbia = sf::read_sf("W:/CMadsen/shared_data_sets/columbia_watershed_priority_area.gpkg") |>
# dplyr::summarise()
# 
# big_boys = dplyr::bind_rows(fras, columbia)
# 
#  ds_limits = sf::st_bbox(st_transform(ds_by_dr_riv,4326))
# 
#  ggplot() +
#    geom_sf(data = big_boys) +
#    geom_sf(data = ds_by_dr_riv) +
#    geom_sf(data = sara_by_dr_river_w_geom, aes(col = Common_Name_EN, fill = Common_Name_EN)) +
#    coord_sf(xlim = ds_limits[c(1,3)],
#             ylim = ds_limits[c(2,4)]) +
#    labs(fill = 'SARA-listed species',
#         col = 'SARA-listed species')
# 
#  sara_by_dr_river |>
#    mutate(draining_river = case_when(
#      draining_river == '100' ~ "Fraser River",
#      draining_river == '300' ~ "Columbia River",
#      T ~ draining_river
#    )) |>
#    sf::st_drop_geometry() |>
#    knitr::kable()
```

```{r}

### SARA species overlap by downstream networks

# all_sara_matched = c("Westslope Cutthroat Trout", "Green Sturgeon", "Mountain Sucker","White Sturgeon","Shorthead Sculpin","Columbia Sculpin","Rocky Mountain Sculpin")
# 
# fras = sf::read_sf(paste0(onedrive_path,"fraser_watershed_priority_area.gpkg")) |>
# dplyr::summarise()
# 
# columbia = sf::read_sf(paste0(onedrive_path,"columbia_watershed_priority_area.gpkg")) |>
# dplyr::summarise()
# 
# # cultus<-zqpm %>% arrange(desc(InvasionRisk)) %>% 
# #   dplyr::select(WATERSH, WATERBO, GNIS_NA, InvasionRisk) %>% 
# #   filter(WATERBO == 329083342) %>% 
# #   dplyr::select(-WATERSH, -WATERBO, -GNIS_NA, -InvasionRisk) %>% 
# #   st_transform(4326)
# 
# big_boys = dplyr::bind_rows(fras, columbia)
# #big_boys<-bind_rows(big_boys, cultus)
# 
# ds_limits = sf::st_bbox(st_transform(ds_by_dr_riv,4326))
# 
#  ggplot() +
#    geom_sf(data = big_boys) +
#    geom_sf(data = ds_by_dr_riv) +
#    geom_sf(data = sara_by_dr_river_w_geom, aes(col = Common_Name_EN, fill = Common_Name_EN)) +
#    coord_sf(xlim = ds_limits[c(1,3)],
#             ylim = ds_limits[c(2,4)]) +
#    labs(fill = 'SARA-listed species',
#         col = 'SARA-listed species')
# 
#  sara_by_dr_river |>
#    mutate(draining_river = case_when(
#      draining_river == '100' ~ "Fraser River",
#      draining_river == '300' ~ "Columbia River",
#      T ~ draining_river
#    )) |>
#    sf::st_drop_geometry() |>
#    knitr::kable()
 
 
```


```{r}
### Table of species by waterbody
# sara_by_wb |>
#    mutate(River = case_when(
#      draining_river == '100' ~ "Fraser River",
#      draining_river == '300' ~ "Columbia River",
#      T ~ draining_river
#    )) |>
#    sf::st_drop_geometry() |>
#    knitr::kable()
```


