---
title: "Whirling Disease - Priority Regions"
author: "Chris Madsen"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
    self_contained: true
    highlight: tango
---
<style type="text/css">
page-inner {
  padding-right: 0px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F)

library(tidyverse)
library(sf)
library(readxl)

WD_sensitive_species_list = str_to_title(c(
    'cutthroat trout',
    'coho salmon',
    'rainbow trout',
    'sockeye salmon',
    'chinook salmon',
    'mountain whitefish',
    'Atlantic salmon',
    'brown trout',
    'bull trout',
    'brook trout'))

SARA_species_list = read_excel('data/SARA-listed_Canadian_FW_fish.xlsx')

# SARA_species_list = c(
#   'cutthroat trout',
#   'White Sturgeon',
#   'bull trout',
#   'sculpin',
#   'pygmy sculpin',
#   'green sturgeon',
#   'mountain sucker',
#   'Nooksack Dace',
#   'Rainbow trout',
#   'Rocky Mountain Ridged Mussel',
#   'Rocky Mountain Sculpin',
#   'Salish Sucker',
#   'Shorthead Sculpin',
#   'Speckled Dace')

species_in_common = WD_sensitive_species_list[WD_sensitive_species_list %in% SARA_species_list$Species]
# species_in_common = c(
#   'Cutthroat Trout',
#   'Rainbow Trout',
#   'Bull Trout'
# )
```

List of fish species identified as sensitive to Whirling disease: `r stringr::str_to_title(paste0(WD_sensitive_species_list, collapse = ', '))`.

List of [Aquatic SARA Schedule-1 listed species](https://www.dfo-mpo.gc.ca/species-especes/sara-lep/cnfasar-fnceap/priority-priorite/profiles/fraser-eng.html#table-schedule1): `r stringr::str_to_title(paste0(SARA_species_list$Species, collapse = ', '))`.

List of species in common between the two lists: `r stringr::str_to_title(paste0(species_in_common, collapse = ', '))`.

```{r read_in_data}
# Point occurrence data for whirling disease-sensitive fish species, data 
# drawn from the BC Data Catalogue fish layer.
occ_dat_b = sf::read_sf('data/sens_fish_sp_occurrence_data.gpkg')

# DFO polygons showing the presence of certain populations of SARA-listed
# and COSEWIC-listed freshwater fish species. Data comes from DFO, 
# for more detail, see script 'download_and_filter_DFO_SARA_occ_data_to_BC.R'
dfo_sara = sf::read_sf('data/dfo_sara_in_col_fras_priority_area.gpkg') |> 
  st_transform(4326) |> 
  st_make_valid()

# Only keep species that are also Aquatic SARA listed species.
occ_dat_b = occ_dat_b |> 
  dplyr::filter(Species %in% species_in_common)

# See number of rows by species
knitr::kable(occ_dat_b |> 
  sf::st_drop_geometry() |> 
  count(Species, sort = T, name = 'count'))

# Filter occ_dat_b for just those points inside the DFO polygons?
occ_dat_b = occ_dat_b |>
  dplyr::filter(sf::st_intersects(geom, sf::st_union(dfo_sara), sparse = F))

# Bring in species at risk layer.
sp = read_sf('W:/CMadsen/Projects/SpeciesAtRisk/species_ecosystems_at_risk_publically_available.shp') |> 
  st_transform(4326)

sp = st_make_valid(sp)

# Make polygon for Fraser River and Colombia River basin polygon
fr = read_sf("W:/CMadsen/shared_data_sets/fraser_watershed_priority_area.gpkg") |> 
  dplyr::summarise()
cl = read_sf("W:/CMadsen/shared_data_sets/columbia_watershed_priority_area.gpkg") |> 
  dplyr::summarise()

pr = fr |> 
  bind_rows(cl) |> 
  dplyr::summarise()

# Federal critical habitat
fch = sf::read_sf('W:/CMadsen/shared_data_sets/DFO_SARA_CriticalHabitat_in_ColFras_Regions.shp')

# Just keep occ_dat and aquatic SAR inside our priority region
occ_dat_f = occ_dat_b |> 
  dplyr::filter(sf::st_intersects(geom, pr, sparse = F))

sp_f = sp |> 
  dplyr::filter(sf::st_intersects(geometry, pr, sparse = F))

# Get surrounding polygons (e.g. Alberta, Washington, rest of BC, etc.)
stateprov_bg = rnaturalearth::ne_states(country = c("Canada","United States of America")) |>
  st_as_sf() |>
  dplyr::select(state_prov = name,
                country = admin) |> 
  dplyr::filter(state_prov %in% c("Washington","British Columbia","Alberta","Idaho","Montana")) |> 
  dplyr::mutate(label = state_prov) |> 
  dplyr::mutate(label = ifelse(label == 'British Columbia',NA,label))

species_dat = dplyr::bind_rows(
  sp_f |> dplyr::select(Species = ENG_NAME_F, 
                        SCI_NAME) |> 
    dplyr::mutate(DataSource = 'Aquatic SAR CDC'),
  occ_dat_f
)
```

```{r make_to_grid}
# library(terra)
# templ_r = terra::rast(pr, res = 0.1)
# 
# # For each species, make a raster according to the raster template.
# sp_polys = occ_dat_f |> 
#   group_by(Species) |> 
#   group_split() |> 
#   lapply(\(x) {
#     this_species = unique(x$Species)
#     st_as_sf(as.polygons(rasterize(x, templ_r))) |> 
#       mutate(Species = this_species)
#     })
# A value of 1 indicates the presence of a given species in that pixel.
grid_geometry = sf::st_make_grid(pr, cellsize = 0.1)

grid_sf = tibble(cell_id = 1:length(grid_geometry)) |>
  st_set_geometry(grid_geometry)

# Mask for just priority region.
grid_sf = grid_sf |> 
  dplyr::filter(sf::st_intersects(geometry, pr, sparse = F))

number_species = sf::st_join(
  occ_dat_f |> 
    dplyr::select(Species),
  grid_sf
) |> 
  sf::st_drop_geometry() |> 
  dplyr::distinct() |> 
  dplyr::group_by(cell_id) |> 
  dplyr::summarise(species_present = paste0(Species, collapse = ', '),
                   number_species = 1 + stringr::str_detect(species_present, ','))
  
grid_sf = grid_sf |> 
  dplyr::left_join(number_species) |> 
  mutate(number_species = replace_na(number_species, 0),
         species_present = replace_na(species_present, 'None'))

grid_sf = grid_sf |> 
  mutate(number_species_f = factor(number_species, levels = c(0,1,2,3)))

grid_cell_res = st_area(grid_sf[1,])/1000000

base_plot = ggplot() + 
  geom_sf(data = stateprov_bg, fill = 'lightgrey',col = 'grey') + 
  geom_sf_text(data = stateprov_bg, aes(label = label), nudge_y = 1) +
  geom_sf(data = pr, fill = 'lightblue') + 
  theme(panel.background = element_rect(fill = 'lightblue'))

```

### Grid of SARA fish species sensitive to Whirling Disease {.tabset}

#### Number of Species
```{r, fig.width=10, fig.height=8}
base_plot + 
  geom_sf(data = grid_sf, aes(fill = number_species_f)) + 
  labs(fill = 'Number of Species',
       title = paste0('Grid resolution: ~',round(grid_cell_res,0),' km^2')) + 
  scale_fill_viridis_d() + 
  coord_sf(xlim = c(-128,-114), ylim = c(48,56.5))
```

#### Species Composition
```{r, fig.width=10, fig.height=8}
base_plot + 
  geom_sf(data = grid_sf, aes(fill = species_present)) + 
  labs(fill = 'Species Composition',
       title = paste0('Grid resolution: ~',round(grid_cell_res,0),' km^2')) + 
  coord_sf(xlim = c(-128,-114), ylim = c(48,56.5))
```

## Grid of SARA species with Provincial Aquatic SAR layer and Federal Critical Habitat layer

```{r, fig.width=10, fig.height=8}
base_plot + 
  geom_sf(data = grid_sf, aes(fill = number_species_f)) +
  geom_sf(data = sp_f, fill = 'darkgreen', col = 'darkgreen') + 
  geom_sf(data = fch, fill = 'red', col = 'red') +
  coord_sf(xlim = c(-128,-114), ylim = c(48,56.5)) +
  labs(title = paste0('Grid resolution: ~',round(grid_cell_res,0),' km^2'),
       fill = 'Abundance of \nSensitive \nFish Species',
       x = 'Longitude', y = 'Latitude',
       caption = 'Aquatic SAR in dark green, SARA Critical Habitat in red') +
  scale_fill_viridis_d()

```

## Interactive Leaflet Map for exploration

```{r}
library(leaflet)

mypal = leaflet::colorNumeric(
  palette = 'Spectral',
  domain = grid_sf$number_species,
  reverse = T
)

mypal_legend = leaflet::colorNumeric(
  palette = 'Spectral',
  domain = grid_sf$number_species,
  reverse = F
)

fch_wgs84 = st_transform(fch, 4326)

leaflet() |> 
  addTiles() |> 
  addMapPane(name = 'SARA_fish', zIndex = 400) |> 
  addMapPane(name = 'Prov_SAR', zIndex = 600) |> 
  addMapPane(name = 'Fed_CH', zIndex = 800) |> 
  addPolygons(data = grid_sf,
              label = ~species_present,
              color = ~mypal(number_species),
              weight = 1,
              fillColor = ~mypal(number_species),
              fillOpacity = 0.65,
              group = 'Sensitive SARA Fish',
              options = pathOptions(pane = 'SARA_fish')) |> 
  addPolygons(data = sp_f,
              fillColor = 'darkgreen',
              fillOpacity = 0.85,
              color = 'darkgreen',
              label = ~ENG_NAME,
              weight = 1,
              group = 'Aquatic Provincial SAR',
              options = pathOptions(pane = 'Prov_SAR')) |> 
  addPolygons(data = fch_wgs84,
              fillColor = 'red',
              fillOpacity = 0.85,
              color = 'red',
              weight = 1,
              group = 'Federal Critical Habitat',
              options = pathOptions(pane = 'Fed_CH')
              ) |> 
  addLegend(pal = mypal_legend,
            values = grid_sf$number_species,
            title = lapply('Number of <br>WD Sensitive <br>SARA Fish <br>Species', htmltools::HTML),
            labFormat = labelFormat(transform = function(x) sort(x, decreasing = TRUE))) |> 
  addScaleBar('bottomright') |> 
  addLayersControl(position = 'bottomleft',
                   overlayGroups = c(
                     'Sensitive SARA Fish',
                     'Aquatic Provincial SAR',
                     'Federal Critical Habitat'),
                   options = layersControlOptions(collapsed = F)) |> 
  leaflet.extras::addResetMapButton()

```

